Motor Learning Without Moving

### 2019-04-26 ManuscriptMaterials.Rmd
restructured for revisions

This document collects statistics and figures to be used in the manuscript on the exposure consequences project.

@@

@@

@@

We've manually selected localization responses that were unlikely to be true responses. Here are the statistics on how many were removed in each dataset. For exposure:

@@

@@

Here is a plot, probably figure 2:

```{r fig3_localization, fig.width=7.5, fig.height=3}
plotLocalization(selectPerformance=selectPerformance,remove15=FALSE)
```

@@

Here are the counts of participants with valid localization estimates in all 4 tasks for every hand angle. Missing data occurs here, because we don't extrapolate beyond the range of the data.

@@

@@

## Is there an effect of exposure training on reach aftereffects?

@@

So this shows that whether or not the feedback was rotated mattered for the reach deviations in the exposure training group, i.e.: there are reach aftereffects.

@@

The second analysis is to show that the reach aftereffects aren't all that different for first and later iterations of the rotated no-cursor tasks. (The rotated data is always compared with _all_ aligned iterations of the task.)

@@

Alternatively, if you want to check the results, you can run this chunk to delete the pre-calculated results, which will force the code to re-calculate it. However, by default, the code here will only use 5000 iterations for bootstrapping, which will ensure that the confidence intervals are less precise than the ones we pre-calculated.

@@

```{r fig5_generalization_maxima, fig.width=7.5, fig.height=3}
plotGeneralization(generateSVG=FALSE,
                   selectPerformance=selectPerformance)
```

@@

There was an interaction between group and hand angle on localization shifts in the LME (far) above, which suggests different generalization curves in the two groups. Here are the confidence intervals for the peaks of the generalization curves for _active_ localization:

```{r localization_peaks}
getPeakLocConfidenceInterval(group='classic',
                             CIs=c(.95), 
                             movementtype='active', 
                             LRpart='all',
                             selectPerformance=FALSE)
getPeakLocConfidenceInterval(group='exposure',
                             CIs=c(.95), 
                             movementtype='active', 
                             LRpart='all', 
                             selectPerformance=selectPerformance)
```

@@

```{r RAE_peaks}
getPeakConfidenceInterval('classic', 
                          part='all', 
                          CIs=c(.95), 
                          selectPerformance=selectPerformance)
getPeakConfidenceInterval('exposure', 
                          part='all', 
                          CIs=c(.95), 
                          selectPerformance=selectPerformance)
```

@@

# #########
# This chunk creates SVG files but shouldn't show up in the PDF / HTML 
# #########

plotLocalization(classicOnline=FALSE,
                 generateSVG=TRUE, 
                 selectPerformance=selectPerformance)
plotReachAftereffects(generateSVG=TRUE,
                      selectPerformance=selectPerformance)
plotGeneralization(generateSVG=TRUE,
                   selectPerformance=selectPerformance)
correlations <- correlateNoCursorsLocalization(generateSVG=TRUE, 
                                               selectPerformance=selectPerformance)
```

>>>>

This document collects statistics and figures to be used in the manuscript on the exposure consequences project. It downloads files from the accompanying Open Science Framework project: [https://osf.io/zfdth/](https://osf.io/zfdth/)

@@

Is the age of this group of participants lower than that of the classic group? We can do a t-test against 24:

```{r age_group_test}
t.test(participants$age, mu=24)

```

@@

So there are also more females now. Let's see if that is significantly different with a binomial exact test:

```{r sex_group_test}
binom.test(x=c(13,8),p=11/21)
```

@@

We've manually selected localization responses that were unlikely to be true responses, and we removed data from reaches where the hand was outside the 0-90 degree span. Here are the statistics on how many were removed in each dataset. For exposure:

@@

## Distribution of data

Let's see how the data is distributed through the workspace. The plot below bins the data, with bins centred on the 7 angles we're interested in, using bins of 10 degrees wide.

```{r loc_bin_counts, fig.width=8, fig.height=5}
plotLocalizationBinCounts()
```

So we have at well over 100 data points close to every hand angle. But we want to know if there are participants without estimates of localization at some points in the workspace. So here are the counts of participants with valid localization estimates in all 4 tasks for every hand angle. Missing data occurs here, because we don't extrapolate beyond the range of the data.

@@

Here is a plot, probably figure 3:

```{r fig3_localization, fig.width=7.5, fig.height=3}
plotLocalization(selectPerformance=selectPerformance,remove15=FALSE,points=c(15,25,35,45,55,65,75))
```

@@

@@

## Localization precision

Many people keep being interested in the precision of active versus passive localization. If active movements before localization result in higher precision, then the variance of the response errors should be lower for active movements. Let's test this in the aligned data for exposure:

```{r exp_loc_var_check}
exp_a <- getLocalizationVariance(group='exposure')
t.test(taperror_deg ~ passive_b, data=exp_a, paired=T)
```

An alternative is to see how many participants were more precise in the active versus the passive localization task, using a binomial exact test. We compare the observed data to a 50% chance which would express the hypothesis that it doesn't matter for localization precision.

```{r}
binom.test( x=sum(aggregate(taperror_deg ~ participant, data=exp_a, FUN=diff)$taperror_deg < 0), n=21, p=.5 )
```

And for the classic group, we do the same:

```{r cla_loc_var_check}
loc_a <- getLocalizationVariance(group='classic')
t.test(taperror_deg ~ passive_b, data=loc_a, paired=T)
binom.test( x=sum(aggregate(taperror_deg ~ participant, data=loc_a, FUN=diff)$taperror_deg < 0), n=21, p=.5 )
```

How about the rotated session for the exposure group:

```{r exp_rot_loc_var_check}
exp_r <- getLocalizationVariance(group='exposure', session='rotated')
t.test(taperror_deg ~ passive_b, data=exp_r, paired=T)
binom.test( x=sum(aggregate(taperror_deg ~ participant, data=exp_r, FUN=diff)$taperror_deg < 0), n=21, p=.5 )
```

Or the rotated session for the classic group:

```{r cla_rot_loc_var_check}
loc_r <- getLocalizationVariance(group='classic', session='rotated')
t.test(taperror_deg ~ passive_b, data=loc_r, paired=T)
binom.test( x=sum(aggregate(taperror_deg ~ participant, data=loc_r, FUN=diff)$taperror_deg < 0), n=21, p=.5 )
```

So in all four cases, making active movements doesn't change the variance: it is neither increased nor decreased. As expected, this confirms all our other tests in previous/upcoming papers.

@@

## Is there an effect of exposure training on open-loop reaches?

@@

So this shows that whether or not the feedback was rotated mattered for the reach deviations in the exposure training group, i.e.: there are reach aftereffects. This means that we subtract the aligned no-cursor reach end-point deviation for each participant and target from the rotated no-cursor reach end-point deviation from the same participant and target, to get the training induced _change_ in reach deviations.

@@

The second analysis is to show that the reach aftereffects aren't all that different for first and later iterations of the rotated no-cursor tasks.

@@

Alternatively, if you want to thoroughly check the results, you can run this chunk to delete the pre-calculated results (set delete=TRUE and download=FALSE), which will force the code to re-calculate it. By default, the code here will use "only" 1000 iterations for bootstrapping, which will run 20 times faster, but also guarantees that the confidence intervals are less precise than the ones we pre-calculated.

@@

```{r fig5_generalization_maxima, fig.width=7.5, fig.height=3}
plotGeneralization(generateSVG=FALSE,
                   selectPerformance=selectPerformance,
                   iterations=200)
```

@@

There was an interaction between group and hand angle on localization shifts in the LME described (far) above, which suggests different generalization curves in the two groups. Here are the confidence intervals for the peaks of the generalization curves for _active_ localization:

```{r localization_peaks}
getPeakLocConfidenceInterval(group='classic',
                             CIs=c(.95), 
                             movementtype='active', 
                             LRpart='all',
                             selectPerformance=selectPerformance,
                             iterations=1000)
getPeakLocConfidenceInterval(group='exposure',
                             CIs=c(.95), 
                             movementtype='active', 
                             LRpart='all', 
                             selectPerformance=selectPerformance,
                             iterations=1000)
```

@@

```{r RAE_peaks}
getPeakConfidenceInterval('classic', 
                          part='all', 
                          CIs=c(.95), 
                          selectPerformance=selectPerformance,
                          iterations=1000)
getPeakConfidenceInterval('exposure', 
                          part='all', 
                          CIs=c(.95), 
                          selectPerformance=selectPerformance,
                          iterations=1000)
```

@@

# #########
# This chunk creates SVG files for all the figures but shouldn't show up in the PDF / HTML 
# #########

plotLocalization(classicOnline=FALSE,
                 generateSVG=TRUE, 
                 selectPerformance=selectPerformance,points=c(15,25,35,45,55,65,75))
plotReachAftereffects(generateSVG=TRUE,
                      selectPerformance=selectPerformance)
plotGeneralization(generateSVG=TRUE,
                   selectPerformance=selectPerformance,
                   iterations=1000)
correlations <- correlateNoCursorsLocalization(generateSVG=TRUE, 
                                               selectPerformance=selectPerformance)
```
